An Extendable \proglang{Python} Implementation of Robust Optimisation Monte Carlo

### 2022-02-14 latex/latex_files/ch4/4-4-extensibility.tex
reordered repo

ROMC can be conceived as a meta-algorithm; it describes a sequence of
steps for approximating the posterior distribution, without
\emph{explicitly} enforcing the methods that solve these steps. Even
though for each step a specific algotihm is proposed
by~\cite{Ikonomov2019}, in general ROMC works well if a practitioner
thinks of an alternative way of approaching a specific
step. Considering this particularity, we designed the implementation
to support such \emph{extensibility} capability.

We have specified four specific points where a user may intervene with
their custom modules; (a) the gradient-based optimization, (b) the
Bayesian Optimization, (c) the proposal region construction and (d)
the surrogate model fitting. These are the four critical parts of the
ROMC procedure, whereas the rest of the code is the backbone of the
algorithm; each of them may be approached with a completely different
algorithm than the one we propose, without the rest of the method to
collapse.

>>>>

ROMC can be conceived as a meta-algorithm; it describes a sequence of
steps for approximating the posterior distribution, without
\emph{explicitly} enforcing the methods that solve these steps. Even
though for each step a specific algorithm is proposed
by~\cite{Ikonomov2019}, in general ROMC is functional if a practitioner
thinks of an alternative way of approaching a specific
step. Considering this particularity, we designed the implementation
to support such \emph{extensibility} capability.

We have specified four specific points where a user may intervene with
their custom modules; (a) the gradient-based optimisation, (b) the
Bayesian Optimisation, (c) the proposal region construction and (d)
the surrogate model fitting. These are the four critical parts of the
ROMC procedure, whereas the rest of the code is the backbone of the
algorithm; each of them can be swapped to a different
algorithm with the same functionality than the one we propose, without the rest of the method to
collapse.

### 2022-02-14 latex/latex_files/images/chapter3/example_posterior.tex
reordered repo

\begin{axis}[
legend cell align={left},
legend style={fill opacity=0.8, draw opacity=1, text opacity=1, draw=white!80!black},
tick align=outside,
tick pos=left,
title={Approximate Posterior},
x grid style={white!69.0196078431373!black},
xlabel={\(\displaystyle \theta\)},
xmin=-3, xmax=3,
xtick style={color=black},
xtick={-3,-2,-1,0,1,2,3},
xticklabels={
  \(\displaystyle {\ensuremath{-}3}\),
  \(\displaystyle {\ensuremath{-}2}\),
  \(\displaystyle {\ensuremath{-}1}\),
  \(\displaystyle {0}\),
  \(\displaystyle {1}\),
  \(\displaystyle {2}\),
  \(\displaystyle {3}\)
},
y grid style={white!69.0196078431373!black},
ylabel={density},
ymin=0, ymax=0.6,
ytick style={color=black},
ytick={0,0.1,0.2,0.3,0.4,0.5,0.6},
yticklabels={
  \(\displaystyle {0.0}\),
  \(\displaystyle {0.1}\),
  \(\displaystyle {0.2}\),
  \(\displaystyle {0.3}\),
  \(\displaystyle {0.4}\),
  \(\displaystyle {0.5}\),
  \(\displaystyle {0.6}\)
}
]
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:-3,0) rectangle (axis cs:-2.88,0);
\addlegendimage{ybar,ybar legend,draw=none,fill=color0,fill opacity=0.5}
\addlegendentry{samples histogram}

>>>>

\begin{axis}[
legend cell align={left},
legend style={fill opacity=0.8, draw opacity=1, text opacity=1, draw=white!80!black, font=\tiny},
tick align=outside,
tick pos=left,
title={Approximate Posterior},
x grid style={white!69.0196078431373!black},
xlabel={\(\displaystyle \theta\)},
xmin=-3, xmax=3,
xtick style={color=black},
xtick={-3,-2,-1,0,1,2,3},
xticklabels={
  \(\displaystyle {\ensuremath{-}3}\),
  \(\displaystyle {\ensuremath{-}2}\),
  \(\displaystyle {\ensuremath{-}1}\),
  \(\displaystyle {0}\),
  \(\displaystyle {1}\),
  \(\displaystyle {2}\),
  \(\displaystyle {3}\)
},
y grid style={white!69.0196078431373!black},
ylabel={density},
ymin=0, ymax=0.6,
ytick style={color=black},
ytick={0,0.1,0.2,0.3,0.4,0.5,0.6},
yticklabels={
  \(\displaystyle {0.0}\),
  \(\displaystyle {0.1}\),
  \(\displaystyle {0.2}\),
  \(\displaystyle {0.3}\),
  \(\displaystyle {0.4}\),
  \(\displaystyle {0.5}\),
  \(\displaystyle {0.6}\)
}
]
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:-3,0) rectangle (axis cs:-2.88,0);
\addlegendimage{ybar,ybar legend,draw=none,fill=color0,fill opacity=0.5}
\addlegendentry{samples histogram}
